---
title: "Homework 1"
author: Alisha Sarakki (aps2204)
output: github_document
---

This is my solution to homework 1

```{r}
library(tidyverse)
```


## problem 1

Create a dataframe with the specified elements

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
mean(pull(prob1_df , samp))
mean(pull(prob1_df , samp_gt_0))
mean(pull(prob1_df , char_vec))
mean(pull(prob1_df , factor_vec))
```

I can take the mean of numbers and logical but not character or factor

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```



## problem 2

# describe the penguins data set
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```

This data describes a sample of 344 penguins taken from the islands of the Palmer Archipelago in Antarctica. Important variables in this data set include penguin species(Adelie, Chinstrap, and Gentoo), island location(Biscoe, Dream, Torgersen), bill length(mean length of 43.92mm), bill depth(mean depth of 17.15mm), flipper length(mean length of 200.9mm), and body mass (mean mass of 4202g). Additional important descriptive information includes the sex of the penguins sampled (165 female, 168 male), and the years in which the study took place (2007-2009). 

```{r}
nrow(penguins)
ncol(penguins)
```

This dataset contains 344 rows and 8 columns. 
The mean flipper length is 200.9mm. 

Below is the plot of bill length(mm) vs. flipper length(mm) of all three species of sampled penguins. 
```{r}

penguins_plot =  ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + xlab("Bill Length (mm)") + ylab("Flipper Length (mm)")

penguins_plot
```

